Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-30 draft/paper1_jenny.tex
Edit 1-D profile

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
          lines correspond to the SMF computed using \mtot{}. 
          Here we separate the HSC massive galaxies into the central galaxies living 
          in halos more massive than \logmh{}$\sim14.2$ (red lines) and the ones in 
          halos with \logmh{}$<14.0$ (black lines).
          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
          very massive halos.
          \textbf{Right}: The stellar mass volume density distributions of massive 
          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
          line). 
          The uncertainty of distribution using \mtot{} is shown in grey shaded 
          region.  
          Here, we also compare the distributions with SMF from previous works: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
          is based on photometry from 2-D \ser{}$+$Exponential model fitting 
          (purple); 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry (blue); 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
          Please see text for more details of the comparison.
          }
      \label{fig:smf}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
    ``total'' stellar mass.

@@

    Compared to the much discussed ``mass-size'' relation, the \mden{} profiles that 
    we have derived capture the full information about the structural properties of 
    massive galaxies. 
    We argue that by studying the shapes of these galaxy profiles directly, we can 
    by-pass outstanding questions about how to accurately define and measure the 
    ``sizes'' and ``masses'' of these massive galaxies. 
    Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
    profiles along with their uncertainties are derived using bootstrap resampling 
    method} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{} 
    bins\footnote{The sample is clearly not complete in the lowest \mtot{} bin, 
    but its median \mden{} profile is still useful to show the overall trend and to 
    compare with previous work}. 
    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
    the \mden{} profiles of these massive galaxies out to 100 kpc 
    \textbf{individually}. 
    These median \mden{} profiles have moderate differences in the inner region, 
    but show significant differences in the outskirts with more massive galaxies 
    showing more prominent stellar envelopes. 
    \jenny{This seems out of place here:Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slowly-rotating 
    (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner isophotal 
    shapes (e.g.\ \citealt{Kormendy2009}), and slightly flattened inner \mden{} 
    profiles (e.g.\ \citealt{Lauer07})}. 
    But in the outskirts, the structure of these galaxies is 
    \emph{clearly not self-similar}. 
    Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
    related to inaccurate sky subtraction. 
    In this paper, we do not use profiles beyond 100 kpc, even though the median 
    \mden{} profiles for the two most massive bins behave reasonably out to 
    ${\sim} 200$ kpc.

    Fig~\ref{fig:avg_prof} compares our results with previous work. 
    Most previous studies have relied on stacking techniques to measure surface 
    brightness profiles out to large radii.
    So far, the surface brightness profiles of massive galaxies out to such large 
    radii was mostly derived via image stacking technique that suffers from several 
    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
    available.

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
          lines correspond to the SMF computed using \mtot{}. 
          Here we separate the HSC massive galaxies into the central galaxies living 
          in halos more massive than \logmh{}$\sim14.2$ (red lines) and the ones in 
          halos with \logmh{}$<14.0$ (black lines).
          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
          very massive halos.
          \textbf{Right}: The stellar mass volume density distributions of massive 
          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
          line). 
          The uncertainty of distribution using \mtot{} is shown in grey shaded 
          region.  
          Here, we also compare the distributions with SMF from previous works: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017}; the \mstar{} 
          is based on photometry from 2-D \ser{}$+$Exponential model fitting 
          (purple); 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry (blue); 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
          Please see text for more details of the comparison.
          }
      \label{fig:smf}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
    ``total'' \mstar{} can have a large impact at the high-mass end.

@@

    Previous discussions about the structural evolution of massive galaxies or the 
    environmental dependence of their structures often focus on scaling relations,  
    like the ``\mstar{}-size'' relation. 
    In this work, we argue that, compared to these scaling relations, the \mden{} 
    profiles that we have derived capture the full structural information of these 
    massive galaxies.
    By studying these \mden{} profiles directly, we can by-pass difficult questions 
    about how to accurately define and measure the ``sizes'' and ``masses'' of these 
    massive galaxies.

    Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
    profiles along with their uncertainties are derived using bootstrap resampling 
    method} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{} 
    bins\footnote{The sample is clearly not complete in the lowest \mtot{} bin, 
    but its median \mden{} profile is still useful to show the overall trend and to 
    compare with previous work}. 
    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
    the \mden{} profiles of these massive galaxies out to 100 kpc 
    \textbf{individually}. 
    These median \mden{} profiles have moderate differences in the inner region. 
    Within inner 10 kpc, the median \mden{} profile of more massive galaxies 
    shows slightly higher \mden{} value but similar slope. 
    These massive galaxies ($\ge 10^{11.4} M_{\odot}$) are known to have quite 
    uniform properties in the inner region. 
    At these masses, most of them should be ``slow-rotating'' 
    (e.g.\ \citealt{Cappellari13b})``core''--elliptical galaxies 
    (e.g.\ \citealt{Lauer07}) that have ``boxy'' inner isophotal shapes and similar 
    slopes of the inner surface brightness profiles (e.g.\ \citealt{Kormendy2009,
    Schombert2015}).

    Meanwhile, in the outskirts, we can notice significant differences where more 
    massive galaxies have gradually more flattened \mden{} profiles and show more 
    prominent stellar halos.
    It is also interesting to see that the distributions of \mden{} profiles show 
    considerably large scatter at large radius. 
    Given the \s2n{} of the HSC image at these surface brightness levels, these 
    scatters should reflect the \textbf{intrinsic scatter of the structures of 
    massive galaxies in their stellar halos}.
    Overall, the structures of massive galaxies are \emph{clearly not self-similar}
    out to 100 kpc. 
    Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
    related to inaccurate sky subtraction. 
    In this paper, we do not use profiles beyond 100 kpc, even though the median 
    \mden{} profiles for the two most massive bins behave reasonably out to 
    ${\sim} 200$ kpc.

    The right panel of Fig~\ref{fig:avg_prof} compares our results with previous 
    works. 
    Most previous studies have relied on stacking techniques to measure surface 
    brightness profiles out to large radii.
    So far, the surface brightness profiles of massive galaxies out to such large 
    radii was mostly derived via image stacking technique that suffers from several 
    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
    available.
